\cvsection{Work Experience}

\begin{cventries}
  \vspace{-2mm}
  \cventry
    {Software Engineer}
    {\href{https://www.kaluza.com/}{Kaluza} (\href{https://www.ovoenergy.com/}{OVO Energy Group})}
    {Lisbon, Portugal (Remote)}
    {June. 2021 - Present}
    {
      \skilltaglist{\textbf{Scala},\textbf{Cats}, \textbf{FS2},Kafka,Terraform,BigQuery,AWS,\textbf{Docker}}
    }

  \cventry
    {Software Engineer}
    {\href{https://www.talkdesk.com/}{Talkdesk}}
    {Lisbon, Portugal}
    {May. 2019 - May. 2021}
    {
      \begin{cvitems}
        % https://talkdesk.com/cloud-contact-center/customer-engagement/outbound-dialer/
        \item \textbf{Designed, built, and launched} \href{https://www.youtube.com/watch?v=W9yJ6gi1ggA}{Outbound Dialer} product (60k phone-calls per Day) - Dialing Engine and Core Telephony components.
        \item \textbf{Doubled the number of calls} launched per minute by the Dialer Engine by optimizing the I/O operations in the critical path.
        \item Designed and built an End to End (E2E) \textbf{Test Automation} Framework to simulate and validate complex Outbound Dialer use cases.
        \item \textbf{Halved deployment time} and improved its safety by automating the process and promoting explicit rollback procedures.
        \item \textbf{Conducted Spring Boot workshops} reducing the time required to onboard new team members.
      \end{cvitems}
      \vspace{4mm}
      \skilltaglist{\textbf{Kotlin},\textbf{Spring Boot},\textbf{Redis},RabbitMQ,PostgreSQL,\textbf{Docker},Kubernetes,Prometheus,Grafana,Telnyx,Twilio}
    }
    
    
  \cventry
    {Software Engineer}
    {\href{https://feedzai.com/}{Feedzai}}
    {Lisbon, Portugal}
    {July. 2017 – May. 2019}
    {
      \begin{cvitems}
        \item \textbf{Designed, built, and launched} Feedzai's Insight product leveraging Elastic Stack for reporting and near real-time dashboards.
        \item Designed, provisioned, and maintained a multi-tenant Elastic Stack solution deployed in AWS and configured using Ansible.
        \item \textbf{Designed data ingestion pipelines} for real-time events (from RabbitMQ) and historical data (from PostgreSQL) using Logstash.
        \item Performed several benchmarks to optimize Feedzai Insights while reducing costs leading to a sizing tool and a set of SLOs.
        %\item Implement a custom authentication and authorization Elastic Search plugins as a proxy to Feedzai's identity provider.
        \item Maintained and provided on-call support to Feedzai for Merchants product.
        %\item Customer Success Engineer to demonstrate Feedzai to a potential US client (3 months).
      \end{cvitems}
      \vspace{4mm}
      \skilltaglist{Java,\textbf{Scala},\href{https://www.elastic.co/elastic-stack}{Elastic Stack},RabbitMQ,PostgreSQL,Akka,\textbf{Docker},AWS,\textbf{Event Processing},Ansible,\href{https://vega.github.io/vega/}{Vega},\href{https://www.tableau.com/}{Tableau}}
    }

  \cventryShort
    {iOS Developer}
    {\href{https://www.carbonbybold.com/pt-pt/}{Carbon By Bold}}
    {Lisbon, Portugal}
    {Dec. 2016 - July. 2017}
%    {\skilltaglist{iOS,Swift,Realm,Objective-C,Core Location,RxSwift,SignalR}}
% Developed and launch 3 iOS applications.

  \cventryShort
    {GSoC iOS Student (\href{https://docs.google.com/presentation/d/1yv4XuNNpTgDkyOjL9SSjGe7PSZuwpbah42mQCACxdXQ/}{2015}) \& GSoC iOS Mentor (\href{https://summerofcode.withgoogle.com/archive/2016/projects/5509901874888704/}{2016}/\href{https://summerofcode.withgoogle.com/archive/2017/projects/5508656065937408/}{2017})}
    {Google Summer of Code (GSoC) participant with \href{http://anitaborg.org/}{AnitaB.org} (Open Source)}
    {Lisbon, Portugal (Remote)}
    {GSoC 2015, 2016, and 2017}
    
  \cventryShort
    {iOS Developer (\href{https://apps.apple.com/us/app/tecnico-lisboa/id959976468}{Técnico Lisboa iOS App})}
    {\href{http://fenixedu.org/}{FenixEdu}}
    {Lisbon, Portugal}
    {Oct. 2014 - Nov. 2015}
%    {\skilltaglist{iOS,Swift,Core Data,Realm,EventKit}}    

\end{cventries}
